%-------------------------
% Rezume, a latex resume template for developers
% Author : Nanu Panchamurthy
% Based off of: https://github.com/sb2nov/resume
% License : MIT

% Hope this resume template helps you land an awesome job. If you found this helpful, please consider starring the github repo here, .
%-------------------------



%------------PACKAGES----------------
\documentclass[a4paper,11pt]{article}

\usepackage{verbatim} % reimplements the "verbatim" and "verbatim*" environments

\usepackage{titlesec} % provides an interface to sectioning commands i.e. custom elements

\usepackage{color} % provides both foreground and background color management

\usepackage{enumitem} % provides control over enumerate, itemize and description

\usepackage{fancyhdr} % provides extensive facilities for constructing headers, footers and also controlling their use

\usepackage{tabularx} % defines an environment tabularx, extension of "tabular" with an extra designator x, paragraph like column whose width automatically expands to fill the width of the environment

\usepackage{latexsym} % provides mathematical symbols

\usepackage{marvosym} % provides martin vogel's symbol font which contains various symbols

\usepackage[empty]{fullpage} % sets margins to one inch and removes headers, footers etc..

\usepackage[hidelinks]{hyperref} % removes color and shadow of hyperlinks

\usepackage[normalem]{ulem} % provides "\ul" (uline) command which will break at line breaks

\usepackage[english]{babel} % provides culturally determined typographical rules for wide range of languages
%-----------------------------------------

\input glyphtounicode % converts glyph names to unicode
\pdfgentounicode=1 % ensures pdfs generated are ats readable

%----------FONT OPTIONS-------------------
\usepackage[default]{sourcesanspro} % uses the font source sans pro
\urlstyle{same} % changes url font from default urlfont to font being used by the document
%-----------------------------------------


%----------MARGIN OPTIONS-----------------
\pagestyle{fancy} % set page style to one configured by fancyhdr
\fancyhf{} % clear all header and footer fields

\renewcommand{\headrulewidth}{0in} % sets thickness of linerule under header to zero
\renewcommand{\footrulewidth}{0in} % sets thickness of linerule over footer to zero

\setlength{\tabcolsep}{0in} % sets thickness of column separator in tables to zero

% origin of the document is one inch from the top and from and the left
% oddsidemargin and evensidemargin both refer to the left margin
% right margin is indirectly set using oddsidemargin
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\topmargin}{-0.5in}

\addtolength{\textwidth}{1.0in} % sets width of text area in the page to one inch
\addtolength{\textheight}{1.0in} % sets height of text area in the page to one inch

\raggedbottom{} % makes all pages the height of current page, no extra vertical space added
\raggedright{} % makes all pages the width of current page, no extra horizontal space added
%------------------------------------------


%--------SECTIONING COMMANDS---------
% \titleformat{<command>}
%   [<shape>]{<format>}{<label>}{<sep>}
%     {<before-code>}[<after-code>]

% command is the sectioning command to be redefined
% shape is the style of the font; scshape stands for small caps style
% format is the format to be applied to whole title- label and text; absent here
% label defines the label
% sep is the horizontal separation between label and title body
% before-code is the code to be executed before
% after-code is the code to be executed after

\titleformat{\section}
  {\scshape\large}{}
    {0em}{\color{blue}}[\color{black}\titlerule\vspace{0pt}]
%-------------------------------------


%--------REDEFINITIONS----------------
% redefines the style of the bullet point
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

% redefines the underline depth to 2pt
\renewcommand{\ULdepth}{2pt}
%-------------------------------------


%--------CUSTOM COMMANDS--------------
%\vspace{} defines a vertical space of given size, modifying this in custom commands can help stretch or shrink resume to remove or add content

% resumeItem renders a bullet point
\newcommand{\resumeItem}[1]{
  \item\small{#1}
}

% commands to start and end itemization of resumeItem, rightmargin set to 0.11in to avoid the overflow of resumetItem beyond whatever resumeItemHeading is being used
\newcommand{\resumeItemListStart}{\begin{itemize}[rightmargin=0.11in]}
\newcommand{\resumeItemListEnd}{\end{itemize}}

% resumeSectionType renders a bolded type to be used under a section, used as skill type here, middle element is used to keep ":"s in the same vertical line
\newcommand{\resumeSectionType}[3]{
  \item\begin{tabular*}{0.96\textwidth}[t]{
    p{0.25\linewidth}p{0.02\linewidth}p{0.71\linewidth}
  }
    \textbf{#1} & #2 & #3
  \end{tabular*}\vspace{-2pt}
}

% resumeTrioHeading renders three elements in three columns with second element being italicized and first element bolded, can be used for projects with three elements
\newcommand{\resumeTrioHeading}[3]{
  \item\small{
    \begin{tabular*}{0.96\textwidth}[t]{
      l@{\extracolsep{\fill}}c@{\extracolsep{\fill}}r
    }
      \textbf{#1} & \textit{#2} & #3
    \end{tabular*}
  }
}

% resumeQuadHeading renders four elements in a two columns with the second row being italicized and first element of first row bolded, can be used for experience and projects with four elements
\newcommand{\resumeQuadHeading}[4]{
  \item
  \begin{tabular*}{0.96\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}
}

% resumeQuadHeadingChild renders the second row of resumeQuadHeading, can be used for experience if different roles in the same company need to added
\newcommand{\resumeQuadHeadingChild}[2]{
  \item
  \begin{tabular*}{0.96\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{\small#1} & {\small#2} \\
  \end{tabular*}
}

% commands to start and end itemization of resumeQuadHeading, lefmargin for left indent of 0.15in for resumeItems
\newcommand{\resumeHeadingListStart}{
  \begin{itemize}[leftmargin=0.15in, label={}]
}
\newcommand{\resumeHeadingListEnd}{\end{itemize}}
%-------------------------------------------


%__________________RESUME____________________
% You can rearrange sections in any order you may prefer
\begin{document}

%-----------CONTACT DETAILS------------------
% Make sure all the details are correct, you can add more links in the first row of second column if needed

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Huge Pablo Cornejo \vspace{2pt}} & % row = 1, col = 1
  Location: Santiago, RM, Chile \\ % row = 1, col = 2
  %\href{https://jane-doe.com}{\uline{jane-doe.com}} $|$ % row = 2, col = 1
  \href{https://www.linkedin.com/in/pablo-cornejo-b4495a223/}{\uline{LinkedIn}} $|$ % row = 2, col = 1
  \href{https://github.com/PabloCornejoM}{\uline{GitHub}} $|$ % row = 2, col = 1
  \href{https://leetcode.com/u/pableto/}{\uline{Leetcode}} & % row = 2, col = 1
  Email: \href{mailto:pablo.cornejo01@gmail.com}{\uline{pablo.cornejo01@gmail.com}} $|$ % row = 2, col = 2
  Mobile: +569 51797058 \\ % row = 2, col = 2
\end{tabular*}
%--------------------------------------------


%-----------SUMMARY--------------------------
% Keep this short, simple and straigth to point

%-----------RESUMEN PROFESIONAL--------------------------

\section{Professional Summary}
\small{
Graduate student in Electrical Engineering with strong interdisciplinary experience across machine learning, data analysis, and deep learning research. Skilled in building end-to-end ML pipelines, developing models for regression, classification, and signal processing, and deploying efficient code in Python and PyTorch. Experienced working in cross-functional teams, leading technical initiatives, and communicating complex concepts clearly. Passionate about applied machine learning, model interpretability, and designing scalable data solutions.
}
%--------------------------------------------

\section{Technical Skills}
  \resumeHeadingListStart{}
  
    \resumeSectionType{Languages}{:}{Python, SQL, C++}

    \resumeSectionType{ML / DL Libraries}{:}{PyTorch, TensorFlow, scikit-learn, NumPy, Pandas}

    \resumeSectionType{Cloud \& MLOps}{:}{AWS, Docker, Git, GitHub}

    \resumeSectionType{ML Techniques}{:}{Deep Learning, Model Training, Feature Engineering}

    \resumeSectionType{Tools}{:}{Jupyter, VSCode, Linux}

  \resumeHeadingListEnd{}

%--------------------------------------------

\section{Languages}
  \resumeHeadingListStart{}

    \resumeSectionType{Languages}{:}{Spanish (Native), English (Professional Proficiency, TOEFL iBT 100)}

  \resumeHeadingListEnd{}



%-----------EXPERIENCE-----------------------
% Distill all your talking points to small bullet points which follow the pattern "challenge-action-result" for maximum efficiency. Try to quantify (use numbers) your points whenver possible, highlist words of importance

\section{Experience}
\resumeHeadingListStart{}

  \resumeQuadHeading{Research Assistant — Visiting Graduate Student}{Mar 2025 -- Present}
  {University of Washington, DiRAC Institute}{Seattle, WA, USA}
    \resumeItemListStart{}
      \resumeItem{Conducting research on symbolic regression methods for astronomical datasets under the supervision of Dr. Andrew Connolly (UW) and Dr. Pablo Estévez (U. of Chile).}
      \resumeItem{Developing neural architectures and training workflows for functional discovery in astrophysical time-series.}
    \resumeItemListEnd{}

  \resumeQuadHeading{ML Research Assistant}{Mar 2023 -- Present}
  {Computational Intelligence Lab, University of Chile}{Santiago, Chile}
    \resumeItemListStart{}
      \resumeItem{Thesis research on neural symbolic regression, focusing on generalization, robustness, and interpretability.}
      \resumeItem{Participation in research projects applying ML to astronomy, medicine, causal theory learning, and mechanical optimization.}
      \resumeItem{Contributed to cross-disciplinary collaborations and presented progress in lab seminars.}
    \resumeItemListEnd{}

  \resumeQuadHeading{Robotics Research Intern}{Dec 2022 -- Mar 2023}
  {CACES Technologies}{Santiago, Chile}
    \resumeItemListStart{}
      \resumeItem{Designed and evaluated a new control architecture for industrial robotic manipulators.}
      \resumeItem{Prototyped algorithms and tested performance in simulated robotic environments.}
    \resumeItemListEnd{}

  \resumeQuadHeadingChild{Robotics Developer Intern}{Dec 2021 -- Feb 2022}
  {PAT Industrial Technologies}{}
    \resumeItemListStart{}
      \resumeItem{Worked on programming and integration of UR and ABB industrial robotic systems for automation solutions.}
    \resumeItemListEnd{}

\resumeHeadingListEnd{}


%---------------------------------------------


%-----------EDUCATION-------------------------
% Mention your CGPA, if its good, in the first row of second column

\section{Education}
  \resumeHeadingListStart{}
    \resumeQuadHeading{Master of Science in Electrical Engineering}{Santiago, Chile}
    {University of Chile. Thesis: \textit{Symbolic Regression via Neural Networks for Scientific Discovery}}{2023 -- 2025}

    \resumeQuadHeading{Bachelor of Science in Electrical Engineering}{Santiago, Chile}
    {University of Chile}{2019 -- 2023}
  \resumeHeadingListEnd{}


%---------------------------------------------


\section{Teaching Assistance}
\resumeHeadingListStart{}

\resumeTrioHeading{Lead Teaching Assistant — Computational Intelligence (2023, 2024)}{Python, ML, Optimization}{University of Chile}
\resumeItemListStart{}
\resumeItem{Led a team of 5 teaching assistants, coordinating tasks, designing assignments, and managing course logistics for 100+ students.}
\resumeItem{Taught core ML concepts including neural networks, optimization, evolutionary algorithms, and hands-on model development in Python. Guided students through practical coding sessions, debugging, and model evaluation workflows.}
\resumeItemListEnd{}

\resumeTrioHeading{Teaching Assistant}{}{University of Chile}
\resumeItemListStart{}
\resumeItem{Experimental Physics (2024), Physics for Architects (2024), Applied Electromagnetism (2022--2023), Digital Systems (2022), Differential and Integral Calculus (2021), Innovation in Electrical Engineering Seminar (2024), Doctoral Seminar (2024), Professional Internship II (2024).}
\resumeItemListEnd{}

\resumeHeadingListEnd{}


%-----------PROJECTS--------------------------
% Use resumeQuadHeading if four elements are feasible (ex: demo video link), else use resumeTrioHeading. Keep the bullet points simple and concise and try to cover wide variety of skills you have used to build these projects

\section{Projects}
  \resumeHeadingListStart{}

    \resumeTrioHeading{Symbolic Regression via Neural Networks}{Python, PyTorch, Feature Selection}{\href{}{\uline{Source Code}}}
\resumeItemListStart{}
  \resumeItem{Initiated and led a research project focused on applying neural network architectures to symbolic regression problems, specifically targeting Nguyen benchmarks.}
  \resumeItem{Developed a hybrid model that integrates neural networks with symbolic regression techniques to accurately fit complex mathematical expressions.}
  \resumeItem{Implemented a custom feature selection algorithm to enhance model efficiency and interpretability, resulting in a improvement in regression accuracy and parsimony.}
  \resumeItem{Conducted comprehensive experiments and analysis, demonstrating the model’s ability to generalize across various symbolic regression tasks.}
\resumeItemListEnd{}

\resumeTrioHeading{Causality and GFlowNets for Brain Signal Recovery}{Python, GFlowNets, Signal Processing}{\href{}{\uline{Source Code}}}
\resumeItemListStart{}
  \resumeItem{Currently developing a novel approach utilizing GFlowNets to recover and denoise brain signals obtained from medical imaging methods such as EEG.}
  \resumeItem{Incorporating causality analysis to model and understand the underlying relationships within noisy brain signal data, enhancing the robustness of signal recovery.}
  \resumeItem{Designed and implemented algorithms aimed at effectively reducing noise and reconstructing high-fidelity brain signals, addressing significant challenges in medical signal processing.}
  \resumeItem{Collaborating with interdisciplinary teams to validate the model’s performance.}
\resumeItemListEnd{}

    
    
    \resumeTrioHeading{Stamp Classifier}{Python, Jupyter Notebook, scikit-learn}{\href{}{\uline{Source Code}}}
    \resumeItemListStart{}
      \resumeItem{Developed and implemented enhancements based on the paper *Alert Classification for the ALeRCE Broker System: The Real-time Stamp Classifier*.}
      \resumeItem{Implemented a random rotation algorithm and conducted feature selection analysis using scikit-learn to boost model performance by 15\%.}
      \resumeItem{Collaborated with a team member to integrate improvements, resulting in a significant increase in SNe classification accuracy.}
      \resumeItem{Addressed data imbalance by implementing advanced augmentation techniques, enhancing model robustness.}
    \resumeItemListEnd{}

  \resumeHeadingListEnd{}
%--------------------------------------------


%----------------OTHERS----------------------
% You can add your acheivements, accolades, certifications etc. here.

\section{Awards \& Honors}
 \resumeHeadingListStart{}
  
  \resumeQuadHeading{University of Chile}{}%
  {Tennis Athlete Distinction}{2021 -- 2023}{Awarded for outstanding participation and performance in the university tennis team.}

  \resumeQuadHeading{}{}%
  {Outstanding Student in Civil and Electrical Engineering}{2019 -- 2023}{Recognized for exceptional academic performance.}

  \resumeQuadHeading{}{}%
  {Best Teaching Assistant — Computational Intelligence}{2024}{Honored for excellence in teaching and course support.}

 \resumeHeadingListEnd{}


%--------------------------------------------

\end{document}